Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions

### 2023-04-28 presentation/index.qmd
we do rm cors instead
plot roc for in-bed

---
title: "Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: false
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

@@

## building Models {transition="convex"}

```{r}
source(here::here("presentation/code/plot_hyperparameter_tuning.R"))

hyper_plot
```

@@

@@

## Many ROC Curves {transition="convex" .H2}

## {transition="convex"}

```{r}
source(here::here("presentation/code/plot_roc_curves.R"))

multi_roc_plot
```

## {transition="convex"}

```{r}
three_classifiers_roc_plot
```

## {transition="convex"}

```{r}
#| fig-width: 8
#| fig-align: center
two_classifiers_roc_plot
```

@@

### Sleep Period Time {.smaller}

```{r}
#| echo: false
source(here::here("presentation/code/plot_ba_metric-wise.R"))

spt_plots[[1]]

spt_plots[[2]]

spt_plots[[3]]

spt_plots[[4]]
```

### Total Sleep Time {.smaller}

```{r}
tst_plots[[1]]

tst_plots[[2]]

tst_plots[[3]]

tst_plots[[4]]
```

### Sleep Effeciency {.smaller}

```{r}
se_plots[[1]]

se_plots[[2]]

se_plots[[3]]

se_plots[[4]]
```

### Latency Until Persistant Sleep {.smaller}

```{r}
lps_plots[[1]]

lps_plots[[2]]

lps_plots[[3]]

lps_plots[[4]]
```

### Wake After Sleep Onset {.smaller}

```{r}
waso_plots[[1]]

waso_plots[[2]]

waso_plots[[3]]

waso_plots[[4]]
```

## Bland-Altman Analysis {transition="convex" .H2}

```{r}
source(here::here("presentation/code/table_ba.R"))

tab_ba_crude
```

## In-bed classification flow {transition="convex" .H2}

```{r}
read_rds(here::here("/media/esbenlykke/My Passport/crude/fitted_models/axed_models/decision_tree_in_bed_AXED.rds")) %>%
  extract_fit_engine() |>
  visTree(
    height = "550px",
    nodesPopSize = TRUE,
    minNodeSize = 10,
    maxNodeSize = 30,
    fallenLeaves = TRUE,
    legend = FALSE,
    digits = 3,
    direction = "UD",
    colorVar = c(
      "#CC5500", "#8B0000", "#FFD700",
      "#228B22", "#654321", "#8B0000", "#FFDB58"
    ),
    export = FALSE
  ) |>
  visNodes(font = list(
    color = "#EEE8D5",
    size = 20,
    strokeWidth = 1
  )) |>
  visEdges(font = list(
    color = "#EEE8D5",
    size = 20,
    strokeWidth = 1
  )) |>
  visInteraction(
    dragNodes = FALSE,
    dragView = FALSE,
    zoomView = FALSE
  )
```

## Sleep classification flow {transition="convex" .H2}

```{r}
read_rds(here::here("/media/esbenlykke/My Passport/crude/fitted_models/axed_models/decision_tree_sleep_AXED.rds")) %>% 
  extract_fit_engine() |>
  visTree(
    height = "550px",
    nodesPopSize = TRUE,
    minNodeSize = 10,
    maxNodeSize = 30,
    fallenLeaves = TRUE,
    legend = FALSE,
    digits = 3,
    direction = "UD",
    colorVar = c(
      "#CC5500", "#8B0000", "#FFD700",
      "#228B22", "#654321", "#8B0000", "#FFDB58"
    ),
    export = FALSE
  ) |>
  visNodes(font = list(
    color = "#EEE8D5",
    strokeWidth = 1
  )) |>
  visEdges(font = list(
    color = "#EEE8D5",
    strokeWidth = 1
  )) |>
  visInteraction(
    dragNodes = FALSE,
    dragView = FALSE,
    zoomView = FALSE
  )
```

# Discussion {transition="convex"}

## Discussion {transition="convex" .smaller}

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds
- could be interesting to build models on thigh and hip ocmbined.
- multiclass vs multilabel classification
- in-bed awake/sleep is highly imbalanced -> maybe train a new classifier accounting for imbalanced data (SMOTE)
- model combined preds instead?

## References {transition="convex"}

>>>>

---
title: "Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: false
    theme: moon
    slide-number: true
    preview-links: auto
    logo: visuals/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

@@

@@

## Sequential Classifiers

![](visuals/chained_models_data_flow.png)

@@

## In-bed models {transition="convex"}

![](visuals/plot_hyper_10.png)

## In-bed performance of decision tree model {transition="convex"}

::: {.column width="60%"}
![](visuals/plot_in_bed_roc.png)
:::

::: {.column width="40%"}
```{r}
source(here::here("presentation/code/tables_performance.R"))

tab_in_bed
```
:::

@@

<!-- ### Sleep Period Time {.smaller} -->

<!-- ```{r} -->
<!-- #| echo: false -->
<!-- source(here::here("presentation/code/plot_ba_metric-wise.R")) -->

<!-- spt_plots[[1]] -->

<!-- spt_plots[[2]] -->

<!-- spt_plots[[3]] -->

<!-- spt_plots[[4]] -->
<!-- ``` -->

<!-- ### Total Sleep Time {.smaller} -->

<!-- ```{r} -->
<!-- tst_plots[[1]] -->

<!-- tst_plots[[2]] -->

<!-- tst_plots[[3]] -->

<!-- tst_plots[[4]] -->
<!-- ``` -->

<!-- ### Sleep Effeciency {.smaller} -->

<!-- ```{r} -->
<!-- se_plots[[1]] -->

<!-- se_plots[[2]] -->

<!-- se_plots[[3]] -->

<!-- se_plots[[4]] -->
<!-- ``` -->

<!-- ### Latency Until Persistant Sleep {.smaller} -->

<!-- ```{r} -->
<!-- lps_plots[[1]] -->

<!-- lps_plots[[2]] -->

<!-- lps_plots[[3]] -->

<!-- lps_plots[[4]] -->
<!-- ``` -->

<!-- ### Wake After Sleep Onset {.smaller} -->

<!-- ```{r} -->
<!-- waso_plots[[1]] -->

<!-- waso_plots[[2]] -->

<!-- waso_plots[[3]] -->

<!-- waso_plots[[4]] -->
<!-- ``` -->

<!-- ::: -->

<!-- ## Bland-Altman Analysis {transition="convex" .H2} -->

<!-- ```{r} -->
<!-- source(here::here("presentation/code/table_ba.R")) -->

<!-- tab_ba_crude -->
<!-- ``` -->

<!-- ## Descriptives of Sleep Quality Statistics Across Methods {transition="convex" .H2 .smaller} -->

<!-- ```{r} -->
<!-- source(here::here("code/evaluate_models/table_descriptives_of_sleep_stats.R")) -->

<!-- tab_descriptives -->
<!-- ``` -->

<!-- ## In-bed classification flow {transition="convex" .H2} -->

<!-- ```{r} -->
<!-- read_rds(here::here("/media/esbenlykke/My Passport/crude/fitted_models/axed_models/decision_tree_in_bed_AXED.rds")) %>% -->
<!--   extract_fit_engine() |> -->
<!--   visTree( -->
<!--     height = "550px", -->
<!--     nodesPopSize = TRUE, -->
<!--     minNodeSize = 10, -->
<!--     maxNodeSize = 30, -->
<!--     fallenLeaves = TRUE, -->
<!--     legend = FALSE, -->
<!--     digits = 3, -->
<!--     direction = "UD", -->
<!--     colorVar = c( -->
<!--       "#CC5500", "#8B0000", "#FFD700", -->
<!--       "#228B22", "#654321", "#8B0000", "#FFDB58" -->
<!--     ), -->
<!--     export = FALSE -->
<!--   ) |> -->
<!--   visNodes(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     size = 20, -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visEdges(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     size = 20, -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visInteraction( -->
<!--     dragNodes = FALSE, -->
<!--     dragView = FALSE, -->
<!--     zoomView = FALSE -->
<!--   ) -->
<!-- ``` -->

<!-- --- -->

<!-- ## Sleep classification flow {transition="convex" .H2} -->

<!-- ```{r} -->
<!-- read_rds(here::here("/media/esbenlykke/My Passport/crude/fitted_models/axed_models/decision_tree_sleep_AXED.rds")) %>%  -->
<!--   extract_fit_engine() |> -->
<!--   visTree( -->
<!--     height = "550px", -->
<!--     nodesPopSize = TRUE, -->
<!--     minNodeSize = 10, -->
<!--     maxNodeSize = 30, -->
<!--     fallenLeaves = TRUE, -->
<!--     legend = FALSE, -->
<!--     digits = 3, -->
<!--     direction = "UD", -->
<!--     colorVar = c( -->
<!--       "#CC5500", "#8B0000", "#FFD700", -->
<!--       "#228B22", "#654321", "#8B0000", "#FFDB58" -->
<!--     ), -->
<!--     export = FALSE -->
<!--   ) |> -->
<!--   visNodes(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visEdges(font = list( -->
<!--     color = "#EEE8D5", -->
<!--     strokeWidth = 1 -->
<!--   )) |> -->
<!--   visInteraction( -->
<!--     dragNodes = FALSE, -->
<!--     dragView = FALSE, -->
<!--     zoomView = FALSE -->
<!--   ) -->
<!-- ``` -->

<!-- # Discussion {transition="convex"} -->

<!-- ## Discussion {transition="convex" .smaller} -->

<!-- - heteroscedasticity -->
<!-- - Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds -->
<!-- - could be interesting to build models on thigh and hip ocmbined. -->
<!-- - multiclass vs multilabel classification -->
<!-- - in-bed awake/sleep is highly imbalanced -> maybe train a new classifier accounting for imbalanced data (SMOTE) -->
<!-- - model combined preds instead? -->

<!-- ## References {transition="convex"} -->
